### 2012-03-14 docs/FAQ/faq.tex
explain what make TAGS and make tags do in the makefiles and how to use them -- very cool feature pointed out by Adam

>>>>

\section{Coding}

\item {\em How do tags work when editing source?}

   Tags allow the editor to follow function/subroutine names an
   automatically switch you to the source code corresponding to that
   function.  Using tags in \maestro\ depends on the editor:

   \begin{itemize}

     \item {\tt vi}:

     In the build directory, type `{\tt make tags}'.  Then in {\tt
       vi}, move the cursor over a function name and use {\tt
       \verb|^|-]} to bring up the source corresponding to that
       function.  Use {\tt \verb|^|-t} to go back.  (Here, {\tt \verb|^|-}
       refers to the Control key.)

     \item {\tt emacs}:

     In the build directory, type `{\tt make TAGS}'.  Then in {\tt
       emacs}, move the cursor over a function name and use {\tt M-.}\
       to bring up the source corresponding to that function.  Use
       {\tt M-*} to go back.  (Here, {\tt M-} refers to the META key.)

   \end{itemize}
